Elephant Seal Age JAE Intraspecific Variation

### 2023-12-07 paper/paperv3.qmd
Adding sample sizes and fixing the initial data filter

sealdat <- read_csv(here::here("data/raw/128L pull 2023_12_05.csv"), 
                    show_col_types = FALSE) %>% 
  mutate(observed = if_else(observed == "B", "Breeder", "Non-breeder"), 
         observed_int = if_else(observed == "Breeder", 1, 0), 
         pup_survived = pupseeneveragain > 0) %>% 
  filter(age > 3, 
         year > 1987)
```

@@

@@

breeding_mod <- glmer(observed_int ~ poly(age, 2) + (1 | animalID) + (1 | year),
                      data = filter(sealdat), 
                      family = "binomial", 
                      control = glmerControl(optimizer = "bobyqa"))

@@

@@

@@

@@

@@

>>>>

sealdat <- read_csv(here::here("data/raw/128L pull 2023_12_05.csv"), 
                    show_col_types = FALSE) %>% 
  mutate(observed = if_else(observed == "B", "Breeder", "Non-breeder"), 
         observed_int = if_else(observed == "Breeder", 1, 0), 
         pup_survived = pupseeneveragain > 0) %>% 
  filter(age > 3, 
         year > 1987)

# 17 observations where pup recruited but did not survive
problem_children <- filter(sealdat, puprecruited == 1 & !pup_survived)

sealdat <- anti_join(sealdat, problem_children, by = c("animalID", "pupID"))
```

@@

n = `r n_distinct(sealdat$animalID)` distinct animals

@@

breeding_mod <- glmer(observed_int ~ poly(age, 2) + (1 | animalID) + (1 | year),
                      data = sealdat, 
                      family = "binomial", 
                      control = glmerControl(optimizer = "bobyqa"))

@@

Sample size n = `r nrow(sealdat)`.

@@

##NOTE: Need to take out the instances where recruitment > survival

@@

Sample size n = `r nrow(surv_recruit_data)`.

@@

Sample size n = `r nrow(pup_sex_data)`.

@@

Sample size n = `r nrow(seal_phenology)`.
